Covariate analysis of UFL-Mayo-ISB RNASeq temporal cortex

### 2016-02-02 code/Rmd/Mayo_TemporalCortex_RNASeq.Rmd
Minor modifications

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(Diagnosis), shape=as.factor(Source), size=as.numeric(AgeAtDeath)))
p <- p + theme_bw() + theme(legend.position="top") 
# p <- p + geom_text(aes(label= ID), size=4, hjust=0)
p
```
```{r decompse.normalise.data2, fig.height=9, fig.width=25, results='asis'}
# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(VOOM.GENE_EXPRESSION$E)), method = "average")
tree = WGCNA::cutreeStatic(sampleTrees, cutHeight = 200, minSize=3)

WGCNA::plotDendroAndColors(sampleTrees, 
                    labels2colors(cbind(tree,COVARIATES)),
                    groupLabels = c('Cluster',colnames(COVARIATES)))
collectGarbage()
dev.off()
```
### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, results='asis', echo=FALSE}
# Find correlation between PC's of gene expression with covariates
DESIGN = getDesignMat2Fact(DM$design,FactorCovariates)
colnames(DESIGN) = substr(colnames(DESIGN),1,50)
preAdjustedSigCovars = runPCAandPlotCorrelations(VOOM.GENE_EXPRESSION$E, DESIGN,
                                                 'NULL design(voom-normalized)',
                                                 isKeyPlot=TRUE)

@@

writeLines(paste('Samples that deviate from others are', paste(sampleTrees$labels[clust==0], collapse = ',')))
```

>>>>

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
dev.off()
```

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(Diagnosis), shape=as.factor(Source), size=as.numeric(AgeAtDeath)))
p <- p + theme_bw() + theme(legend.position="top") 
# p <- p + geom_text(aes(label= ID), size=4, hjust=0)
p
```
```{r decompse.normalise.data2, fig.height=9, fig.width=25, results='asis'}
# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(VOOM.GENE_EXPRESSION$E)), method = "average")
tree = WGCNA::cutreeStatic(sampleTrees, cutHeight = 135, minSize=10)

WGCNA::plotDendroAndColors(sampleTrees, 
                    labels2colors(cbind(tree,COVARIATES)),
                    groupLabels = c('Cluster',colnames(COVARIATES)))
collectGarbage()
dev.off()

tmp = paste('Samples in cluster 0 are', paste(sampleTrees$labels[tree == 0], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
tmp = paste('Samples in cluster 2 are', paste(sampleTrees$labels[tree == 2], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
```
### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, results='asis', echo=FALSE}
# Find correlation between PC's of gene expression with covariates
DESIGN = getDesignMat2Fact(DM$design,FactorCovariates)
colnames(DESIGN) = substr(colnames(DESIGN),1,50)
preAdjustedSigCovars = runPCAandPlotCorrelations(VOOM.GENE_EXPRESSION$E, DESIGN,
                                                 'NULL design(voom-normalized)',
                                                 isKeyPlot=TRUE)

@@

tmp = paste('Samples in cluster 0 are', paste(sampleTrees$labels[tree == 0], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
```
